---
title: "Turkish Cities Cinema Rate"
author: "ISY"
date: "1/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE,warning = FALSE)
```

## Introduction

This documents shows a map for Turkish cities' going-cinema rate in 2019. Data had been obtained from Google Maps for coordinates and https://www.tuik.gov.tr for city information.

## Part 0: Setup

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(leaflet)
```


## Part 1: Preparing Data

Data had been download preliminary because of language difference. There are two different datasets: one for coordinates and one for city information.


```{r}
data <- read.csv(file = paste0(getwd(), "/", "filmWatch.csv"), sep = ";")
coords <- read.csv(file = paste0(getwd(), "/", "turkishcitiescoord.csv"), sep = ";")
```

Let's check both datasets. To check if we have any 0 values, we will arrange the dataset.

```{r}
data %>% arrange(numFilm) %>% head()
```

```{r}
head(coords)
```
As we can see, there are some cities with 0 values. We will create their data manually later.

## Part 3 : Setting New Variables and Combining Datasets

We will calculate each cities watching density, which is "density of people per film". Note that since we have 0 values in dataset, we will manually change them later. 

```{r}
# Arrange both datasets according to city names alphabeticaly.

data <- data %>% arrange(cityName)
coords <- coords %>% arrange(city)

#Watching Density Calculation

data$watchDens <- data$numPeople / data$numSeat / data$numFilm

#
nan_val <- grepl(NaN, data$watchDens)
data[nan_val,][["watchDens"]] <- 0

```

Let's mutate *lng* and *lat* variables to our main data. 

```{r}
data$lng <- coords$lng
data$lat <- coords$lat
```

Finally, lets create color codes for density intervals so we can use them in our legend. Our colors will be:

- Gray: Fifth Interval. This color will mean that closing a couple of cinemas or reducing seats must be considered.
- White: Forth Interval. This color will mean that closing a a couple of cinemas or reducing seats should be considered.
- Green: Third Interval. This color will mean that the proportion is OK. Investment could be made on maintenance of cinemas.
- Yellow: Second Interval. This color will mean that a entreprenur can make investment in cinema building.
- Red: First Interval. This color will mean that a entrepreneur should make investment in cinema building.

```{r}
densityint <- cut(data$watchDens, 5)
data$densityInt <- densityint
int_levels <- levels(densityint)

#Create dummy variable for color

data$color <- NA

#Create color codes

for (i in 1:nrow(data)) {
     if (data$densityInt[i] == int_levels[5]) {
          data$color[i] <- "gray" 
     } 
     
     if (data$densityInt[i] == int_levels[4]) {
          data$color[i] <- "white"
     }
     if (data$densityInt[i] == int_levels[3]) {
          data$color[i] <- "green"
     }
     
     if (data$densityInt[i] == int_levels[2]) {
          data$color[i] <- "yellow"
     }
     
     if (data$densityInt[i] == int_levels[1]) {
          data$color[i] <- "red"
     }
}
```

## Part 5: Creating Map

Since we have prepared our data, we will now create the map

```{r}
data %>% leaflet() %>% 
     addTiles() %>% 
     addMarkers(popup = c(data$cityName), clusterOptions = markerClusterOptions(), 
                label = paste("Number of People: ", "\n", data$numPeople, "Number of Seats:", "\n", data$numSeat, "Number of Films:", "\n", data$numFilm),
                labelOptions = labelOptions(interactive = TRUE, )) %>%
     addCircles(weight = 15, color = data$color, radius = data$numPeople/(1E5*2)) %>%
     addLegend(labels = c("Should Make Investment", "Should Consider Reduction", "Can Consider Reduction", "Can Consider Investment", "OK"), colors = unique(data$color))



```

## Appendix

This is not a worked-on project. I just wanted to show what can be done with leaflet library. Decision-making through this data should not be done :D. 
